### 2022-04-28 draft.tex
add sources and tiny section on history

\renewcommand{\contentsname}{Inhaltsverzeichnis}
\renewcommand{\refname}{Quellenangabe}
\renewcommand{\figurename}{Abbildung}
\graphicspath{ {./res/} }

@@

\pagenumbering{arabic}
\setcounter{page}{3}
\section{Einführung}

	\newpage

 \section{Fazit}

@@

@@

@@

\section{Anhang}

>>>>

\graphicspath{ {./res/} }

@@

\pagenumbering{arabic}
\setcounter{page}{3}
\section{Introduction}

	\newpage
\section{History}

While initial speculation about genetics dates back to Hippocrates and Aristotle, who developed theories to explain inheritance\cite{mayr}, it was not until 1856 when Gregor Mendel experimented with cross breeding numerous pea plants to discover patterns in attribute inheritance\cite{mendel}, not knowing his actions would plant a seed within biology that would soon bloom to disrupt areas of daily life far beyond the bounds of science.
	\newpage

 \section{Conclusion}

@@

\bibitem{mayr} Mayr, Ernst,
\textbf{The Growth of Biological Thought} (Belknap Press, 1985)

\bibitem{mendel} Mendel, Gregor
\textbf{Experiments in Plant Hybridization} (Read at the meetings of February 8th, and March 8th, 1865)

@@

\bibitem{rawal} Rawal, Leena \& Ali, Sher,
\textbf{Genome Analysis and Human Health} (Springer Singapore 2017)

@@
